The Rockerverse: Packages and Applications for Containerisation with R

### 2020-02-25 manuscript.Rmd

**\pkg{dockr}** ([https://github.com/smaakage85/dockr](https://github.com/smaakage85/dockr)) is a very similar package attempting to mirror a given R session, including local non-CRAN packages\citep{kjeldgaard_dockr_2019}.
Users can manually add statements for non-R dependencies to the `Dockerfile`.

@@

The ordering of authors following DN and DE is alphabetical.
DN conceived the article idea, \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}, wrote sections not mentioned below, and revised all sections.
DB wrote the section on \pkg{outsider}.
GD contributed the CARD.com use case.
DE wrote the introduction and the section about containerisation and Rocker Project, and reviewed all sections.
RC \& EH contributed to the section on interfaces for Docker in R (_dynverse_ and `dynwrap`).
DC contributed content on Gigantum.
ME contributed to the section on processing and deployment to cloud services.
CF wrote paragraphs about \pkg{r-online}, \pkg{dockerfiler}, \pkg{r-ci} and \pkg{r-db}.
SL contributed content on RStudio's usage of Docker.
BM wrote the section on research compendia and made the project Binder ready.
HN \& JN co-wrote the section on the T-Mobile use case.
KR wrote the section about \pkg{holepunch}.
NR wrote paragraphs about shared work environments and GPUs.
LS \& NT wrote the section on Bioconductor.
CW wrote the sections on Whole Tale and contributed the publication reproducibility audit use case.
NX contributed content on \pkg{liftr}.
All authors approved the final version.
This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page}, \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history}, and \href{https://github.com/nuest/rockerverse-paper/issues/}{discussion issues} provide a detailed view on the respective contributions.

>>>>

**\pkg{dockr}** ([https://github.com/smaakage85/dockr](https://github.com/smaakage85/dockr)) is a similar package focusing on the generation of Docker images for R packages, in which the package itself and all of the R dependencies, including local non-CRAN packages, are available \citep{kjeldgaard_dockr_2019}.
\pkg{dockr} facilitates the organisation of code in the R package structure and the resulting Docker image mirrors the package versions of the current R session.
Users can manually add statements for non-R dependencies to the `Dockerfile`.

@@

The ordering of authors following DN and DE is alphabetical.
DN conceived the article idea, \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}, wrote sections not mentioned below, and revised all sections.
DB wrote the section on \pkg{outsider}.
GD contributed the CARD.com use case.
DE wrote the introduction and the section about containerisation and Rocker Project, and reviewed all sections.
RC \& EH contributed to the section on interfaces for Docker in R (_dynverse_ and `dynwrap`).
DC contributed content on Gigantum.
ME contributed to the section on processing and deployment to cloud services.
CF wrote paragraphs about \pkg{r-online}, \pkg{dockerfiler}, \pkg{r-ci} and \pkg{r-db}.
SL contributed content on RStudio's usage of Docker.
BM wrote the section on research compendia and made the project Binder ready.
HN \& JN co-wrote the section on the T-Mobile use case.
KR wrote the section about \pkg{holepunch}.
NR wrote paragraphs about shared work environments and GPUs.
LS \& NT wrote the section on Bioconductor.
CW wrote the sections on Whole Tale and contributed the publication reproducibility audit use case.
NX contributed content on \pkg{liftr}.
LK contributed content on \pkg{dockr}.
All authors approved the final version.
This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page}, \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history}, and \href{https://github.com/nuest/rockerverse-paper/issues/}{discussion issues} provide a detailed view on the respective contributions.
